A simplified Plackett-Luce likelihood function for rank orders

### 2024-03-28 inst/hankin-ejs.tex
typo

One long-standing contention in the athletic world is that of lane
bias~\cite{munro2022}.  Running in the inner lane is frequently held
to be a disadvantage; mechanisms include biomechanical issues arising
from centrifugal acceleration, to competitors' inability to see their
rivals.  Here attention is restricted to heats, for which lane placing
is random.  I consider every heat in Men's 100m Olympic running from
2004-2020 (a total of 41 heats, each of 8 or 9 competitors); only
competitors' ranks are used.  Figure~\ref{plotolymp} shows a
log-likelihood curve for the Bradley-Terry strength of the focal
competitor, here the runner in the innermost lane.  We see that the
evaluate of $0.574$ is very close to the neutral value of $0.5$, for
which the support is only $0.16$, far short of Edwards's two units of
support criterion for rejection~\cite{edwards1972}.  This dataset
contains no evidence to support lane bias.

>>>>

One long-standing contention in the athletic world is that of lane
bias~\cite{munro2022}.  Running in the inner lane is frequently held
to be a disadvantage; mechanisms include biomechanical issues arising
from centrifugal acceleration, to competitors' inability to see their
rivals.  Here attention is restricted to heats, for which lane placing
is random.  I consider every heat in Men's 100m Olympic running from
2004-2020 (a total of 41 heats, each of 8 or 9 competitors); only
competitors' ranks are used.  Figure~\ref{plotolymp} shows a
log-likelihood curve for the Bradley-Terry strength of the focal
competitor, here the runner in the innermost lane.  We see that the
evaluate of $0.474$ is very close to the neutral value of $0.5$, for
which the support is only $0.16$, far short of Edwards's two units of
support criterion for rejection~\cite{edwards1972}.  This dataset
contains no evidence to support lane bias.
